---
title       : Corpus Processing Methods II
subtitle    : An R-chitecture Introduction
author      : Shu-Kai Hsieh 謝舒凱
job         : GIL, National Taiwan University
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
github:
  user: loperntu
  repo: corpusProcessingMethods
---

## Introduction: Data, Data, Data!

> 1. Decision is YOURS: English teacher or (Linguistic) Data Scientist
2. Write using R Markdown
3. Use an empty line followed by three dashes to separate slides!

--- 

## CPM, 到底有什麼特別?

> 1. Linguistics: a data-intensive discipline? 
> 2. Corpus data science
> 3. Pre-processing
> 4. (Corpus-based) Exploratory Data Analysis 
> 5. Hypothesis and Testing
> 6. Statistical Modeling
> 7. Demo: Shiny-LexicoR 

---

## Motion Chart

```{r echo = F, results='asis', message = F}
require(googleVis)
M1 <- gvisMotionChart(Fruits, idvar = 'Fruit', timevar = 'Year')
print(M1,tag = 'chart')
```

---

## ggplot2

```{r echo = F, results='asis', message = F}
require(ggplot2)
head(diamonds)
ggplot(diamonds, aes(clarity, fill=cut)) + geom_bar()
```

---
