---
title       : Corpus Processing Methods II
subtitle    : An R-chitecture Introduction
author      : Shu-Kai Hsieh 謝舒凱
job         : GIL, National Taiwan University
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
github:
  user: loperntu
  repo: corpusProcessingMethods
---

## Introduction: Data, Data, Data!

> 1. "Data are values of qualitative or quantitative variables, belonging to a set of items (i.e., populations)." (wiki)
> 2. Linguistics: a data-intensive discipline? 
> 3. The Decision is YOURS: English teacher or (Linguistic) Data Scientist

--- 

## What's so special about CPM ? OR, What do you mean by *processing* data? 

In general, Corpus data science involves a chain of works

> 1. Pre-processing (cleaning, tokenizing, segmentation, etc)
> 2. Data annotation (Semi-automatic) Labeling (POS tagging) and Management
> 3. Exploratory Data Analysis (with workable knowledge of Statistics)
> 4. Hypothesis testing
> 5. Prediction, Statistical Modeling, etc
> 6. Web application (Demo: Shiny-LexicoR) 

---

## **Empirical method and statistics**

```
are two sides of the same coin: it is pointless to study one without the other. (You simply cannot design an experiment and interpret the results without understanding what the data are telling you and what they do not and–even more importantly – cannot tell you.)
```
---


## R Self Warm-up Quiz ( from R. Peng)

- Download the dataset on http://www.biostat.jhsph.edu/~rpeng/coursera/selfquiz/selfquiz-data.csv and load it into R with the read.csv function. Assign the output of read.csv to an object named dataset. 

> Possible solutions 


```{r echo = T, results='asis', message = F}
## One way (easiest and fastest)
dataset <- read.csv("http://www.biostat.jhsph.edu/~rpeng/coursera/selfquiz/selfquiz-data.csv")

## You may want to store a local copy for later
download.file("http://www.biostat.jhsph.edu/~rpeng/coursera/selfquiz/selfquiz-data.csv","selfquiz-data.csv")
dataset <- read.csv("selfquiz-data.csv")
```

---

## R Self Warm-up Quiz (level 1)

- What are the column names of the data frame?
- What are the row names of the data frame?
- Extract the first 6 rows of the data frame and print them to the console.
- How many observations (i.e. rows) are in this data frame?

> Possible solutions 

```{r echo = T, results = 'hide', message = F}
## 
names(dataset)  ## colnames(dataset) also works
## 
rownames(dataset)
## 
head(dataset, 6)  ## print(dataset[1:6, ]) 
##
nrow(dataset)

```

---

## R Self Warm-up Quiz (level 2)

- Extract the last 6 rows of the data frame and print them to the console
- How many missing values are in the "Ozone" column of this data frame?
- What is the mean of the "Ozone"" column in this dataset? Exclude missing
values (coded as NA) from this calculation.
- Extract the subset of rows of the data frame where Ozone values are above
31 and Temp values are above 90.


> Possible solutions 

```{r echo = T, results = 'hide', message = F}
##
tail(dataset)
## 37
miss <- is.na(dataset[, "Ozone"]) ## A vector of TRUE/FALSE
sum(miss)
## 42.13
mean(dataset[, "Ozone"], na.rm = TRUE)
##
subset(dataset, Ozone > 31 & Temp > 90)
```

---

## R Self Warm-up Quiz (level 3)

- Use a for loop to create a vector of length 6 containing the mean of each
column in the data frame (excluding all missing values).
- Use the apply function to calculate the standard deviation of each column
in the data frame (excluding all missing values).


```{r echo = T, results = 'hide', message = F}
##
m <- numeric(6)
for (i in 1:6) {
m[i] <- mean(dataset[, i], na.rm = TRUE)
}
##
s <- apply(dataset, 2, sd, na.rm = TRUE)
print(s)
print(m)
```

---

## R Self Warm-up Quiz (level 4)

- Calculate the mean of "Ozone" for each Month in the data frame and
create a vector containing the monthly means (exclude all missing values).


```{r echo = T, message = F}
tapply(dataset$Ozone, dataset$Month, mean, na.rm = TRUE)
```

> - Draw a random sample of 5 rows from the data frame.

```{r echo = T, results='hide', message = F}
set.seed(1) ## Just so the answer is repeatable
dataset[sample(nrow(dataset), 5), ]

```

---



